---
title: "Pitfalls in Student Report Assignments"
subtitle: "How Spurious Correlations Distort Empirical Findings"
date: today
date-format: full
author:
  - name: "Hirotaka Fukui"
    email: "227e127e@gsuite.kobe-u.ac.jp"
    affiliations:
      - name: "Kobe University, Graduate School of Economics"
execute: 
  echo: false
  warning: false
  message: false
format: typst
engine: knitr #knitr for R, jupyter for Python
brand:
  typography:      
    fonts:
      - family: Noto Serif JP
        source: google
      - family: IBM Plex Sans JP
        source: google
    base: Noto Serif JP
    headings:
      family: IBM Plex Sans JP
      weight: regular
number-sections: true
---

# Introduction

In many introductory economics or statistics courses, students are often asked to analyze publicly available data and “find correlations” between variables. While such assignments appear pedagogically useful, they can unintentionally lead students to misinterpret correlations as economically meaningful relationships.

Time-series data in particular are prone to spurious correlations, where two variables appear strongly correlated simply because they both follow similar upward or downward trends. Without appropriate statistical techniques, students may draw incorrect causal conclusions and reinforce misunderstandings about empirical methods.

This report highlights these risks through a simple empirical demonstration and proposes improvements in assignment design.

# Case Study: When Assignments Mislead

```{r}
#| label: setup
#| include: false

install.packages(c("tseries", "ggplot2", "dplyr", "lmtest", "patchwork"))
library(tseries)
library(ggplot2)
library(dplyr)
library(lmtest)
library(patchwork)
```

```{r}
# 数値ベクトル
dat = c( 1, 2, 4, 8, 16, 32 )

# plot 関数で図が出力される
plot( dat )
```
